Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
small text about the full res experiment

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step.

\begin{table}
  \begin{center}
%    \begin{tabular}{@{}lrrrrrrrrrrr@{}}
%      \toprule
%      & \multicolumn{5}{c}{$R=8$}   & \multicolumn{6}{c}{$R=16$}\\
%      \cmidrule(r){2-12}
%    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
%      \midrule
%      Number of texture fetches &
%      1468 & 2 & 28 & 260 & 2104 &
%      5706 & 2 & 28 & 90 & 2120 & 1780\\
%      Time (in ms) &
%      208 & 15 & 26 & 93 & 642 &
%      826 & 14 & 26 & 252 & 606 & 4801\\
%      $L_\infty$ error (\wrt $l_0$) &
%      0.051 & 0.306 & 0.085 & 0.047 & 0 &
%      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
%      $L_2$ error (\wrt $l_0$) &
%      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0 &
%      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
%      \bottomrule
%    \end{tabular}

>>>>

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step. We compare the approximation made to accelerate 
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}.

We can first see that the number of texel fetch required to compute
the curvature reduces drastically when computing the approximations.
This is mandatory if we want to increase the framerate.
However, we can also note that the error increases quite slowly. 
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to 
the $l_0$ level.
Thanks to this low error, higher approximation levels are visually 
very similar to the $l_0$ level. We can therefore use them for exploring our 
datasets in real time, changing the radii on the fly and visualising dynamic datasets.

Bare in mind that those results were measured on a full resolution triangulation.
Since we compute the curvature of each vertices of the final mesh, a highly triangulated object will
be much slower to process.
We therefore use in practice an adaptive triangulation of the object, refining the mesh
when it is closer from the camera and thus reducing the number of vertices to compute.

\begin{table}
  \begin{center}
